Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-05-01 Paper Sigatoka - 2015.tex
Correcciones de estilo y sugerencias

@@

@@

\title{Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques 
%\tnoteref{mytitlenote}
}
%\tnotetext[mytitlenote]{Fully documented templates are %available in the elsarticle package on \href{http://%www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}%{CTAN}.}

@@

\author[afiCorbana] {Mauricio Guzmán-Quesada}
\author[afiCorbana]{José-Antonio Guzmán-Alvarez}
\author[afiPablo]{Pablo Alvarado-Moya}

@@

Black Sigatoka, disease caused by the fungus Mycosphaerella fijiensis
Morelet, is the main problem phytopathologic of banana and plantain
crops in Central America \citep{MarinVargas1995}.

This disease attacks the leaves of plants producing a rapid deterioration of the leaf area. It affects the growth and productivity of plants by decreasing photosynthetic capacity. Also causes a reduction in quality of the fruit \citep{MarinVargas1995}.

The climate has a major effect on the behavior of the black Sigatoka. Precipitation, temperature, relative humidity and wind are the main climatic variables affecting the development of this disease \citep{MarinVargas1995}.

@@

The early warning system for black Sigatoka is an adaptation of the yellow Sigatoka warning system developed by Ganry and Meyer and modified by Ganry and Laville to use for controlling yellow Sigatoka in Cameroon. Ternesien and Fouré  later improved Ganry and Laville's system.
%
The latter system is based on weekly observations of disease symtoms on young leaves of the plant, according to Fourés symptom (stages) descriptions. Arbitrary coefficientes, based on incidence and severity of disease development, are used to calculate two variables: gross sum and state of evolution.
%
Gross sum is based on the stage present and an arbitrary coefficient, which increases with the advance of the symptoms and the juvenility of the leaf. The state of evolution is calculated using the gross sum and the foliar emission period.
%
Although threshold levels were initially suggested as a guide to spray timing, the fluctuation of these two variables was found to better define appropiate times to spray \citep{Marinetal2003}.

\subsubsection{Support Vector Regression (SVR)}
From the perspective of Support Vector Regression (SVR) the regression function $y = f(s)$ for a given dataset $D=\{(s_i,y_i)\}_{i=1}^n$ , is represented as a linear function of the form \citep{Wei2013}:
$$f(s)=w^Ts+b$$
where $w$ and $b$ are respectively the weight vector and the intercept of the model, and they are selected to find an optimal fit to the data available in $D$.

>>>>

\usepackage{color}
\definecolor{dkred}{rgb}{0.5,0,0}       %   dark red
\definecolor{todocolor}{rgb}{1.0,0.8,0.5}

@@

\newcommand{\todohdr}{Please review:}
\newcommand{\TODO}[2][\todohdr]{%
\smallbreak\noindent\colorbox{todocolor}{%
\begin{minipage}{1\linewidth}
\textbf{#1}\par{\footnotesize{#2}}
\end{minipage}}}

\newcommand{\instead}[2]{\textcolor{dkred}{\st{#1}}#2}

@@

\title{Forecasting the black Sigatoka development rate:\\ 
A comparison of machine learning techniques}

@@

\author[afiCorbana]{Mauricio Guzmán-Quesada}
\author[afiCorbana]{José-Antonio~Guzmán-Alvarez}
\author[afiPablo]{Pablo Alvarado-Moya}

@@

The black Sigatoka is a disease caused by the fungus
\emph{Mycosphaerella fijiensis Morelet}.  It is the main
phytopathologic problem of banana and plantain crops in Central
America \citep{MarinVargas1995}.
%
This disease attacks the plant leaves producing a rapid deterioration
of the leaf area. It affects the growth and productivity of the
affected plant by impairing its photosynthetic capacity, which
consequently causes a reduction in quality of the fruit
\citep{MarinVargas1995}.

The climate has a major effect on the development of the black
Sigatoka.  Precipitation, temperature, relative humidity and wind are
the main climatic variables affecting the development of this disease
\citep{MarinVargas1995}.

@@

\TODO{Revisar si la nueva redacción de este párrafo coincide con la
  original.  Eso es lo que creo se quería decir, porque no quedaba
  claro cuál sistema fue creado por quién...  Las referencias a cada
  sistema en algo así son absolutamente necesarias.  Favor reemplazar
  \citep{XXX} por las referencias correspondientes (Pablo, 1/5/16)}

The early warning system developed by Ganry and Meyer \citep{XXX} for
the control of the yellow Sigatoka in Cameroon was adapted by Ganry
and Meyer \citep{XXX} for the black Sigatoka. 
%
%The early warning system for black Sigatoka \citep{XXX} is an
%adaptation of the yellow Sigatoka warning system developed by Ganry
%and Meyer \citep{XXX}.  It was modified by Ganry and Laville
%\citep{XXX} for its ito use for controlling yellow Sigatoka in
%Cameroon.
Ternesien and Fouré \citep{XXX} later improved Ganry and Laville's system.

The latter system is based on weekly quantified observations of
the disease progression on young leaves of the plant, according to
Fouré's scale of the symptom stages.
%
The numeric coefficients describe the degree of incidence and the
severity of the disease development.  These coefficients are used to
calculate two variables: gross sum and state of evolution.
\TODO{coefficients??  No suena como coeficientes (un factor que
  multiplica términos en una función) sino como una calificación o
  nota o algo así (quizá ``grade''?).  ``Arbitrary coefficient'' no
  tiene sentido por el ``arbitrary''... No creo que sean tan
  arbitrarios sino predefinidos.  De hecho, el párrafo que sigue dice
  que suben con el avance de síntomas, es decir, no es tan
  ``arbitrario''.  Quizá querés decir ``arbitrarily chosen''?.  No
  estoy seguro si entiendo lo que se quiere decir aquí.}

The gross sum is based on the present disease progression stage and 
\instead{an arbitrary coefficients}{the arbitrarily chosen grading},
which increases with the advance of the symptoms and the
juvenility of the leaf.
%
The state of evolution is calculated using the gross sum and the
foliar emission period.
%
Although threshold levels were initially suggested as a guide to spray
\instead{timing}{schedules}, the fluctuation of these two variables
was found to better define appropiate times to spray
\citep{Marinetal2003}.

\subsubsection{Support Vector Regression (SVR)}

From the perspective of Support Vector Regression (SVR) the regression function $y = f(s)$ for a given dataset $D=\{(s_i,y_i)\}_{i=1}^n$ , is represented as a linear function of the form \citep{Wei2013}:
$$f(s)=w^Ts+b$$
where $w$ and $b$ are respectively the weight vector and the intercept of the model, and they are selected to find an optimal fit to the data available in $D$.
